Reduced growth due to belowground sink limitation is not fully explained by reduced photosynthesis

### 2017-03-03 manuscript/editor_response2_tree_physiology.Rmd
finsihed editor comments#2

\
*Response*:

@@

\
*Response*:

@@

\
*Response*:

@@

\
*Response*:

>>>>

\
*Response*: corrected *A*~n~ to *P*~day~

@@

\
*Response*: We have added two citations in relation to the functional balance hypothesis of plant biomass partitioning.

@@

\
*Response*: We have replaced *A*~n~ with *P*~day~ as this sentence refers to total net seedling C gain.

@@

\
*Response*: There was not an error here (caption).  However, "total plant leaf mass" was replaced with "total leaf mass" for simplicity.

### 2017-03-03 manuscript/manuscript_pve_editor.Rmd
finsihed editor comments#2

\
It was further necessary to calculate a self-shading parameter ($\sigma$) when scaling leaf *A*~n~ with total plant leaf area. This was accomplished by utilizing 61 previously digitized *Eucalyptus* seedlings, covering 5 total species which include *E. tereticornis*, from Duursma *et al.* [-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC] in R to build a 3D plant structure based on digitized metrics of plant allometry and crown structure. Using the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A*~n~, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf. The ratio of total *A*~n~ with self-shading to horizontal leaf was then used to calculate $\sigma$ for each of the 61 digitized seedlings, independently for each of the seven soil volume treatments. Next, the linear relationship between $\sigma$ and total leaf area was determined across digitized seedlings, within each treatment. For the growth model, $\sigma$ was then predicted for each daily time step using the previous days cumulative leaf area and this value was then applied to *P*.

@@

##Biomass partitioning under sink limitation
As biomass partitioning is likely controlled by the source and sink strength of all organs [@poorter2012biomass], it was important to determine which tissue components were most affected by the container size treatments. It was necessary to distinguish if growth was affected beyond ontogenetic constraints, by correcting for size, as biomass distribution is strongly size-dependent [@gould1966allometry; @lleonart2000removing]. In this study, there was no significant difference in root, leaf, or stem biomass partitioning with reduced soil volume compared to Free seedlings, once ontogenetic drift was taken into account (Figure `r allocfig`a,b). A conserved ratio of fine root mass to leaf mass was observed across all treatments, suggesting that seedlings maintained homeostasis with biomass partitioning instead of a functional partitioning response to optimize limiting soil resources.

@@

##Do reductions in photosynthesis explain reductions in seedling growth?
We use a simple approach to estimate cumulative seedling C gain with measured reductions in leaf photosynthetic parameters, via soil volume effects.  Although reductions in both *A*~max~ and biomass were correlated among treatments, as hypothesized by Poorter *et al.* [-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *A*~n~ do not fully explain reduced seedling growth. As estimated whole-plant C use efficiency was decreased in containerized seedlings, this suggests that other components of the C balance were affected. These results are especially noteworthy for process-based growth models that parameterize CUE, tissue respiration and C allocation as fixed processes. For example, classical approaches in tree growth and production modelling are often driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation]. It is possible these results represent an initial overestimation of *A*~n~, however, the robust empirical based methods used to generate photosynthetic parameters (*J*~max~, *V*~cmax~, *R*~dark~ and *g*~1~) make this unlikely. Instead, our results indicate a need to evaluate how oversimplified representations of processes other than *A*~n~ affect models which distinguish the fate of assimilate C within a plant. Doing so will provide valuable input to future models as assimilate allocation is a key component in C-balance driven plant growth models [@lacointe2000carbon].

@@

```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=600,eval=includeFigs}
source("master_scripts/allometryplotting.R")
```  
**Figure 1**. Seedling growth over the duration of the experiment was strongly reduced in containerized seedlings compared to freely rooted seedlings. Height growth (a), diameter growth (b), and seedling leaf area estimated from leaf counts (c) measured weekly on *Eucalyptus tereticornis* seedlings across the experiment duration in 2013. Shown are soil volume treatment means &pm; standard error.
\
```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600,eval=includeFigs}
source("master_scripts/airvars_plotting.R")
```  
**Figure 2**. Environmental drivers over the course of the experiment. Daily maximum and minimum temperature (a), total daily PPFD (b), and daily maximum vapour pressure deficit (c) in 2013. 
\
```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=600,eval=includeFigs}
source("master_scripts/allocation_plotting.R")
```  
**Figure 3**. Biomass partitioning at final harvest did not respond strongly to soil volume treatment. (a) Relative partitioning to leaves, stems, and roots at the final harvest, shown as treatment means (standard errors omitted for clarity). (b) Bi-variate relationships between mass partitioning to leaves and stems + roots. Each symbol is a plant. Lines represent standardized major axis fitting of the log-transformed allometric relationships of leaf mass fraction by treatment. (c) Total plant leaf mass as a function of fine root biomass with &pm; standard error. The dashed line is a 1:1 line and the solid line represents the significant log-log model fit (*R*^2^ = 0.82) with equation: log(x) = -0.36 + 0.983 * log(y).
\
```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, eval=includeFigs}
source("master_scripts/Amax_TNC_N_plotting2.R")
```  
**Figure 4**. Photosynthetic capacity on a leaf mass basis (A~mass~, measured at saturating light and [CO~2~]) was correlated to both leaf starch and nitrogen content. (a) A~mass~ was negatively related to leaf starch (shown as percentage of dry mass), in particular for leaves with higher nitrogen content (N~mass~). (b) A~mass~ was positively related to N~mass~ (expressed as N per unit mass after subtracting TNC content). In both panels, each symbol is an individual measurement of A~mass~ (data across all campaigns are shown). Colors represent bins levels (n = 5) of both leaf starch and nitrogen grouped from low to high. Lines represents predictions, for each bin level, from the linear mixed effects model equation of A~mass~ as a function of starch and nitrogen. The marginal *R*^2^ (fixed effects only) was 0.37 and the conditional *R*^2^ (fixed and random effects) was 0.48 for the complete model. The equation for the full model is y = - 221.96 + 28.58(N) - 3.31(Starch) - 0.87(N*Starch).
\
```{r cuefig, fig.width=6, fig.height=6, echo=FALSE, dev="png", dpi=600, eval=includeFigs}
source("master_scripts/cuefig.R")
```  
**Figure 5**. The final biomass attained per unit total photosynthesis over the duration of the experiment. Note the higher ratio for the freely rooted seedlings compared to the containerized seedlings, indicating a higher carbon-use efficiency. Shown are treatment means, as the model scaling instantaneous leaf photosynthesis to total plant photosynthesis was run once for every treatment.

>>>>

\
It was further necessary to calculate a self-shading parameter ($\sigma$) when scaling *P*~day~ with total plant leaf area. This was accomplished by utilizing 61 previously digitized *Eucalyptus* seedlings, covering 5 total species which include *E. tereticornis*, from Duursma *et al.* [-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC] in R to build a 3D plant structure based on digitized metrics of plant allometry and crown structure. Using the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A*~n~, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf. The ratio of total *A*~n~ with self-shading to horizontal leaf was then used to calculate $\sigma$ for each of the 61 digitized seedlings, independently for each of the seven soil volume treatments. Next, the linear relationship between $\sigma$ and total leaf area was determined across digitized seedlings, within each treatment. For the growth model, $\sigma$ was then predicted for each daily time step using the previous days cumulative leaf area and this value was then applied to *P*.

@@

##Biomass partitioning under sink limitation
As biomass partitioning is likely controlled by the source and sink strength of all organs [@poorter2012biomass], it was important to determine which tissue components were most affected by the container size treatments. It was necessary to distinguish if growth was affected beyond ontogenetic constraints, by correcting for size, as biomass distribution is strongly size-dependent [@gould1966allometry; @lleonart2000removing]. In this study, there was no significant difference in root, leaf, or stem biomass partitioning with reduced soil volume compared to Free seedlings, once ontogenetic drift was taken into account (Figure `r allocfig`a,b). A conserved ratio of fine root mass to leaf mass was observed across all treatments, suggesting that seedlings maintained homeostasis with biomass partitioning instead of a functional partitioning response to optimize limiting soil resources [i.e. @davidson1969effect; @shipley2002balanced].

@@

##Do reductions in photosynthesis explain reductions in seedling growth?
We use a simple approach to estimate cumulative seedling C gain with measured reductions in leaf photosynthetic parameters, via soil volume effects.  Although reductions in both *A*~max~ and biomass were correlated among treatments, as hypothesized by Poorter *et al.* [-@poorter2012pot], we provide evidence that the negative effects of sink limitation on *P*~day~ do not fully explain reduced seedling growth. As estimated whole-plant C use efficiency was decreased in containerized seedlings, this suggests that other components of the C balance were affected. These results are especially noteworthy for process-based growth models that parameterize CUE, tissue respiration and C allocation as fixed processes. For example, classical approaches in tree growth and production modelling are often driven by inputs of C assimilation and processes such as respiration are considered proportional to biomass [@le2001carbon] or growth rate [@tjoelker1999acclimation]. It is possible these results represent an initial overestimation of *A*~n~, however, the robust empirical based methods used to generate photosynthetic parameters (*J*~max~, *V*~cmax~, *R*~dark~ and *g*~1~) make this unlikely. Instead, our results indicate a need to evaluate how oversimplified representations of processes other than *A*~n~ affect models which distinguish the fate of assimilate C within a plant. Doing so will provide valuable input to future models as assimilate allocation is a key component in C-balance driven plant growth models [@lacointe2000carbon].

@@

```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=600,eval=includeFigs}
source("master_scripts/allometryplotting.R")
```  
**Figure 1**. Seedling growth over the duration of the experiment was strongly reduced in containerized seedlings compared to freely rooted seedlings. Height growth (a), diameter growth (b), and seedling leaf area estimated from leaf counts (c) measured weekly on *Eucalyptus tereticornis* seedlings across the experiment duration in 2013. Shown are soil volume treatment means &pm; standard error.
\
```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600,eval=includeFigs}
source("master_scripts/airvars_plotting.R")
```  
**Figure 2**. Environmental drivers over the course of the experiment. Daily maximum and minimum temperature (a), total daily PPFD (b), and daily maximum vapour pressure deficit (c) in 2013. 
\
```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=600,eval=includeFigs}
source("master_scripts/allocation_plotting.R")
```  
**Figure 3**. Biomass partitioning at final harvest did not respond strongly to soil volume treatment. (a) Relative partitioning to leaves, stems, and roots at the final harvest, shown as treatment means (standard errors omitted for clarity). (b) Bi-variate relationships between mass partitioning to leaves and stems + roots. Each symbol is a plant. Lines represent standardized major axis fitting of the log-transformed allometric relationships of leaf mass fraction by treatment. (c) Total leaf mass as a function of fine root biomass with &pm; standard error. The dashed line is a 1:1 line and the solid line represents the significant log-log model fit (*R*^2^ = 0.82) with equation: log(x) = -0.36 + 0.983 * log(y).
\
```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, eval=includeFigs}
source("master_scripts/Amax_TNC_N_plotting2.R")
```  
**Figure 4**. Photosynthetic capacity on a leaf mass basis (A~mass~, measured at saturating light and [CO~2~]) was correlated to both leaf starch and nitrogen content. (a) A~mass~ was negatively related to leaf starch (shown as percentage of dry mass), in particular for leaves with higher nitrogen content (N~mass~). (b) A~mass~ was positively related to N~mass~ (expressed as N per unit mass after subtracting TNC content). In both panels, each symbol is an individual measurement of A~mass~ (data across all campaigns are shown). Colors represent bins levels (n = 5) of both leaf starch and nitrogen grouped from low to high. Lines represents predictions, for each bin level, from the linear mixed effects model equation of A~mass~ as a function of starch and nitrogen. The marginal *R*^2^ (fixed effects only) was 0.37 and the conditional *R*^2^ (fixed and random effects) was 0.48 for the complete model. The equation for the full model is y = - 221.96 + 28.58(N) - 3.31(Starch) - 0.87(N*Starch).
\
```{r cuefig, fig.width=6, fig.height=6, echo=FALSE, dev="png", dpi=600, eval=includeFigs}
source("master_scripts/cuefig.R")
```  
**Figure 5**. The final biomass attained per unit total photosynthesis over the duration of the experiment. Note the higher ratio for the freely rooted seedlings compared to the containerized seedlings, indicating a higher carbon-use efficiency. Shown are treatment means, as the model scaling instantaneous leaf photosynthesis to total plant photosynthesis was run once for every treatment.
